Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-25 content.tex
Implementing feedback reviewer: references should have correct capitalization

BEAST [\cite{drummond2007beast}] is a typical Bayesian phylogenetics tool, 
that needs both character data and priors to infer 
a posterior distribution of phylogenies.
Specifically, for the species tree prior - which describes 
the process of diversification - 
BEAST has built-in priors such as the Yule [\cite{yule}] and 
(constant-rate) birth-death [\cite{nee1994reconstructed}] models.
These simple tree priors are the most commonly used, as they have sufficient biological complexity, while being computationally fast.
BEAST's successor, BEAST2 [\cite{bouckaert2019beast}],
has a package manager, that allows third-party users 
to extend existing functionalities.
For example, one can add novel diversification models 
by writing a BEAST2 package that contains the likelihood 
formula of a phylogeny under the novel diversification model, 
i.e. the prior probability of a species tree.
Many diversification models (and their associated probability algorithms) have been developed, e.g., models in which diversification is time-dependent [\cite{nee1994reconstructed}, \cite{rabosky2008explosive}], 
or diversity-dependent [\cite{etienne2011diversity}],
or where diversification rates change for specific lineages 
and their descendants [\cite{etienne2012conceptual}, 
\cite{rabosky2014automatic}, \cite{alfaro2009nine}, 
\cite{laudanno2020sls}], models that treat speciation as a process that takes 
time [\cite{rosindell2010protracted}][\cite{etienne2012prolonging}][\cite{lambert2015reconstructed}], 
or as a burst of simultaneous branching
events [\cite{laudanno2018mbd}], or where diversification rate
depends on a trait that has two [\cite{maddison2007estimating}], 
or more [\cite{fitzjohn2012diversitree}] states,
even concealed states [\cite{beaulieu2016detecting}] 
or a combination of all these [\cite{herrera2018detecting}].

Many diversification models (and their associated probability algorithms) have been developed to account for possible mechanisms.
There are models in which diversification rates are time-dependent [\cite{nee1994reconstructed}, \cite{rabosky2008explosive}], 
or diversity-dependent [\cite{etienne2011diversity}],
or not homogeneous across the entire phylogeny [\cite{etienne2012conceptual}, 
\cite{rabosky2014automatic}, \cite{alfaro2009nine}, 
\cite{laudanno2020sls}], models that treat speciation as a process that takes time [\cite{rosindell2010protracted}][\cite{etienne2012prolonging}][\cite{lambert2015reconstructed}], 
or as a burst of simultaneous branching
events [\cite{laudanno2018mbd}].
Others account for trait-dependent regimes, in several ways: where diversification rates
depend on a trait that has two [\cite{maddison2007estimating}], 
or more [\cite{fitzjohn2012diversitree}] states,
even concealed states [\cite{beaulieu2016detecting}] 
or a combination of all these [\cite{herrera2018detecting}].
Despite such a rich theoretical landscape, only a few of these diversification models are available as a BEAST2 package.

@@

The goal of \verb;pirouette; is to quantify the importance of a tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the true model that generated the given tree
as the 'generative tree model' $\mathit{p_{G}}$.
We define the birth-death (BD) model [\cite{nee1994reconstructed}] as
the standard tree model, as many (non-standard) tree models 
have a parameter setting for which they reduce to this model. 
One such example is the diversity-dependent (DD) tree 
model [\cite{DDD, etienne2011diversity}]:
the DD model is a BD model with a speciation rate that is dependent 
on the number of species and a carrying capacity. For a carrying capacity
of infinity, the DD model reduces to a BD model.
When benchmarking a novel tree model, 
one will typically construct phylogenies 
for different combinations of the diversification model's parameters, 
to assess under which scenarios the inference error cannot be neglected. 
While we recommend many replicate simulations 
when assessing a novel tree prior, 
our examples contain only one replicate,
as the goal is to show the workings of \verb;pirouette;,
instead of doing an extensive analysis.
The supplementary materials, however, do show the results
of replicated runs under multiple settings.

@@

  \begin{tabular}{|@{}c|p{4cm}|p{12.2cm}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Symbol} &
    \textbf{Macro-argument} &
    \textbf{Description} \\
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{G}$ &
    Generative model &
    The full setting to produce BEAST2 input data. 
    Its core features are the tree prior $\mathit{p_{G}}$, the clock 
    model $\mathit{c_{G}}$ and the site model $\mathit{s_{G}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
    $\mathit{A}$ &
    Alignment model &
    It includes the parts of the generative model that directly affect the 
    alignment generation, like the clock model $\mathit{c_{G}}$ and 
    the site model $\mathit{s_{G}}$. Additional arguments can be provided, 
    such as the mutation rate and the root sequence. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{X_{i}}$ &
    $i$-th candidate experiment &
    Full setting for a Bayesian inference. It is made by a 
    candidate inference model $\mathit{I_{i}}$ and its 
    inference conditions $\mathit{C_{i}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{I}$ &
    Inference model &
    Phylogenetic inference model to run BEAST2. Likewise the generative model $G$, 
    its main components are the tree prior $\mathit{p_{I}}$, 
    the clock model $\mathit{c_{I}}$ and the site model $\mathit{s_{I}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{C}$ & Inference conditions & Conditions under which $\mathit{I}$ 
    is used in the inference. 
    They are composed by the model type, run condition and 
    whether to measure the evidence. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{E}$ & Error measure parameters & 
    Errors measurement setup that can be specified providing an 
    error function to measure the difference between the original phylogeny 
    and the inferred posterior. The initial part of the posterior that is 
    reckoned as not representative can be discarded using a burn-in fraction. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline 
  \end{tabular}
  \caption{
    Definitions of terms and relative symbols used in the main text and in 
    Fig~\ref{fig:pipeline}. To run the pipeline $\mathit{A}$, $\mathit{X}$ 
    and $\mathit{E}$ must be specified. Examples can be found in 
    listings~\ref{lst:create_alignment_params}, 
    \ref{lst:create_gen_experiment_explicit} and 
    \ref{lst:create_error_measure_params}.
  }
  \label{tab:definitions}
\end{sidewaystable}

@@

\begin{figure}
  \centering
  \includegraphics[width = \textwidth]{workflow4.png}
  \caption{
    \texttt{pirouette} pipeline.
    The pipeline starts from a phylogeny (1a) simulated by the generative tree model 
    $\mathit{p_{G}}$.
    The phylogeny is converted to an alignment (2a) using the generative alignment model 
    $\mathit{A} = (\mathit{c_{G}}, \mathit{s_{G}})$, composed of a clock and a site model. 
    The user defines one or more experiments.
    For each candidate experiment $\mathit{X_{i}}$ 
    (a combination of inference model $\mathit{I_{i}}$ and condition $\mathit{C_{i}}$),
    if its condition $\mathit{C_{i}}$ is 
    satisfied (which can depend on the alignment), 
    the corresponding inference model $\mathit{I} = \mathit{I_{i}}$ is selected
    to be used in the next step.
    The inference models (3a) of the selected experiments use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using the error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, for each selected inference model a twin pipeline can be run.
    A twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using the twin tree model $\mathit{p_{t}}$, 
    selected among standard diversification models; 
    the default option is the standard BD model, 
    with parameters estimated from the original phylogeny.
    A twin alignment (2b) is then simulated from the twin phylogeny 
    using clock model $\mathit{c_{G}}$ and site model $\mathit{s_{G}}$ 
    imported from the generative model. 
    The twin alignment has the same number of mutations as the original alignment.
    The twin pipeline follows the procedure of the main pipeline, 
    resulting in a twin error distribution (5b).
  }
  \label{fig:pipeline}
\end{figure}

@@

The second step (Fig.~\ref{fig:pipeline}, 3a)
selects one (or more) inference model(s) $I$ from a set of inference models $I_{1},\dots,I_{n}$. 
We define an experiment $X_{i}$ as the combination of 
an inference model $I_{i}$ and the conditions $C_{i}$ 
to actually use it in the inference step.
For example, we may require that an inference
model (a combination of a tree model, clock model and site model) 
should include the generative/true tree model. 
As a second example, we may require that we have selected a set of 
candidate inference models,
of which only the best should be used in the actual inference.
In the first example, we specified the condition $C_{i}$ that this
generative model should always be run, whereas in the second example,
we specified condition $C_{i}$ that a candidate model should only be run
when it is the best.
The 'best' model is defined as the inference model with
the highest evidence (a.k.a. marginal likelihood), based on the alignment 
simulated in the previous step.
The evidence for an inference model is estimated by nested 
sampling [\cite{russel2019model}], using the \verb;NS; BEAST2 package.

@@

An optional step is to use the 'twinning process'.
This process, $T$, encompasses two steps:
$T_1$, that generates a 'twin tree' (Fig.~\ref{fig:pipeline}, 1b) 
and $T_2$, which generates a 'twin alignment' (Fig.~\ref{fig:pipeline}, 2b).
Both twin tree and alignment will be analyzed in the same way 
as the true tree and alignment.

@@

The twin pipeline serves as a control: 
even when the generating model matches the assumed inference model
(as is the case in the twin pipeline),
the inferred trees from the posterior distribution will 
still differ from the true tree, 
due to stochasticity in producing an alignment 
and to the MCMC sampling of the posterior.
The twin pipeline provides this minimum error,
because the generating and inference model match exactly.
When comparing the true and twin error distribution,
any differences will be due to the fact that true and twin phylogenies 
are realizations of different processes: one (possibly) non-standard, $p_G$, 
and one standard, $p_T$ (see Fig~\ref{fig:pipeline}).

@@

The user has to specify exactly one standard inference model,
but may be insure which one to pick. To account for this, the user can
specify a set of candidate inference models. After a true alignment
has been simulated, the candidate model with the highest evidence will be
used in another inference run, resulting in another error distribution.
If twinning is used, a candidate model that has the highest evidence for
the twin alignment, this model is also used to create another error
distribution. Thanks to the use of candidate models, one can check
if the generative model picked, has been a good choice.

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    The inference error made 
    for both a generative tree prior and best candidate model
    compared with the error obtained for the twin tree.
    Here, the 'twin' tree shows the baseline inference error.
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

Focussing on the upper panel of Figure \ref{fig:example_30},
we can see that the error distributions of the generative model
differ strongly between the true and twin tree. 
This difference shows the extent of the mismatch between
the actual tree model (which is DD) and the (BD) tree prior used.
Because these distributions are distinctively different,
the inference error we make when using an 
incorrect (that is, BD) tree prior on a DD tree
is profound.

@@

@@

We showed how to use \verb;pirouette; to quantify the importance of a 
tree prior in Bayesian phylogenetics, using the simplest generative tree 
model possible.
In principle any other (more complex) generative tree model can be tested, 
but we chose to provide the simplest (and fastest to run) examples.

Figure~\ref{fig:example_30} illustrates the primary result of our pipeline: 
it shows the error distributions for the true tree and the twin tree 
when either the generating model or the best candidate model is used in inference. 
The clear difference between the error distributions 
for the true tree and the twin tree suggests 
that the choice of tree prior does matter.
We note, however, that only one tree from a novel tree model
is not enough to determine the impact of using an incorrect
tree prior. Instead, a distribution 
of multiple trees, generated by the novel tree model, should be used.

In conclusion, \verb;pirouette; can show the errors to be expected
when the tree prior used in inference is different from the generating model.
The user can then judge whether or not a new tree prior, 
tailored on the generative process, is needed. 
If this is indeed the case, one can implement 
the novel tree prior as an addition to 
his/her favorite Bayesian inference tool.

>>>>

BEAST [\cite{drummond2007beast}] is a typical Bayesian phylogenetics tool, 
that needs both character data and priors to infer 
a posterior distribution of phylogenies.
Specifically, for the species tree prior - which describes 
the process of diversification - 
BEAST has built-in priors such as the Yule [\cite{yule}] and 
(constant-rate) birth-death [\cite{nee1994reconstructed}] models.
These simple tree priors are the most commonly used, as they have sufficient biological complexity, while being computationally fast.
BEAST's successor, BEAST2 [\cite{bouckaert2019beast}],
has a package manager, that allows third-party users 
to extend existing functionalities.
For example, one can add novel diversification models 
by writing a BEAST2 package that contains the likelihood 
formula of a phylogeny under the novel diversification model, 
i.e. the prior probability of a species tree.
Many diversification models (and their associated probability algorithms) 
have been developed, e.g., models in which diversification is time-dependent [\cite{nee1994reconstructed,rabosky2008explosive}],
or diversity-dependent [\cite{etienne2011diversity}],
or where diversification rates change for specific lineages 
and their descendants [\cite{etienne2012conceptual, rabosky2014automatic, alfaro2009nine}].
Other models treat speciation as a process that takes 
time [\cite{rosindell2010protracted, etienne2012prolonging, lambert2015reconstructed}],
or where diversification rate
depends on one or more traits [\cite{maddison2007estimating, fitzjohn2012diversitree}].
Despite such a rich theoretical landscape, only a few of these 
diversification models are available as a BEAST2 package.

@@

The goal of \verb;pirouette; is to quantify the importance of a tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree
as the 'generative tree model' $\mathit{p_{G}}$.
We define the birth-death (BD) model [\cite{nee1994reconstructed}] as
the standard tree model, as many (non-standard) tree models 
have a parameter setting for which they reduce to this model. 
One such example is the diversity-dependent (DD) tree 
model [\cite{DDD, etienne2011diversity}]:
the DD model is a BD model with a speciation rate that is dependent 
on the number of species and a carrying capacity. For a carrying capacity
of infinity, the DD model reduces to a BD model.
When benchmarking a novel tree model, 
one will typically construct phylogenies 
for different combinations of the diversification model's parameters, 
to assess under which scenarios the inference error cannot be neglected. 
While we recommend many replicate simulations 
when assessing a novel tree prior, 
our examples contain only one replicate,
as the goal is to show the workings of \verb;pirouette;,
instead of doing an extensive analysis.
The supplementary materials, however, do show the results
of replicated runs under multiple settings.

@@

  \begin{tabular}{|@{}c|p{4cm}|p{12.2cm}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Symbol} &
    \textbf{Macro-argument} &
    \textbf{Description} \\
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{G}$ &
    Generative model &
    The full setting to produce BEAST2 input data. 
    Its core features are the tree prior $\mathit{p_{G}}$, the clock 
    model $\mathit{c_{G}}$ and the site model $\mathit{s_{G}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
    $\mathit{A}$ &
    Alignment model &
    Specifies the alignment generation, such as the clock model 
    $\mathit{c_{G}}$, site model $\mathit{s_{G}}$ and root sequence. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{X_{i}}$ &
    $i$-th candidate experiment &
    Full setting for a Bayesian inference. It is made by a 
    candidate inference model $\mathit{I_{i}}$ and its 
    inference conditions $\mathit{C_{i}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{I}$ &
    Inference model &
    The assumed phylogenetic inference model, of which the main components
    are the tree prior $\mathit{p_{I}}$, assumed clock model $\mathit{c_{I}}$ 
    and assumed site model $\mathit{s_{I}}$. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{C}$ & Inference conditions & Conditions under which $\mathit{I}$ 
    is used in the inference. 
    They are composed by the model type, run condition and 
    whether to measure the evidence. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    $\mathit{E}$ & Error measure parameters & 
    Errors measurement setup that can be specified providing an 
    error function to measure the difference between the original phylogeny 
    and the inferred posterior. The initial part of the posterior that is 
    reckoned as not representative can be discarded using a burn-in fraction. \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline 
  \end{tabular}
  \caption{
    Definitions of terms and relative symbols used in the main text and in 
    Fig~\ref{fig:pipeline}. To run the pipeline $\mathit{A}$, $\mathit{X}$ 
    and $\mathit{E}$ must be specified. Examples can be found in 
    listings~\ref{lst:create_alignment_params}, 
    \ref{lst:create_gen_experiment_explicit} and 
    \ref{lst:create_error_measure_params}.
  }
  \label{tab:definitions}
\end{sidewaystable}

@@

\begin{figure}
  \centering
  \includegraphics[width = \textwidth]{workflow4.png}
  \caption{
    \texttt{pirouette} pipeline.
    The pipeline starts from a phylogeny (1a) simulated by the 
    generative tree model 
    $\mathit{p_{G}}$.
    The phylogeny is converted to an alignment (2a) using the generative 
    alignment model 
    $\mathit{A} = (\mathit{c_{G}}, \mathit{s_{G}})$, composed of a clock and a site model. 
    The user defines one or more experiments.
    For each candidate experiment $\mathit{X_{i}}$ 
    (a combination of inference model $\mathit{I_{i}}$ and condition $\mathit{C_{i}}$),
    if its condition $\mathit{C_{i}}$ is 
    satisfied (which can depend on the alignment), 
    the corresponding inference model $\mathit{I} = \mathit{I_{i}}$ is selected
    to be used in the next step.
    The inference models (3a) of the selected experiments use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using the error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, for each selected inference model a twin pipeline can be run.
    A twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using the twin tree model $\mathit{p_{t}}$, 
    selected among standard diversification models; 
    the default option is the standard BD model, 
    with parameters estimated from the original phylogeny.
    A twin alignment (2b) is then simulated from the twin phylogeny 
    using clock model $\mathit{c_{G}}$ and site model $\mathit{s_{G}}$ 
    imported from the generative model. 
    The twin pipeline follows the procedure of the main pipeline, 
    resulting in a twin error distribution (5b).
  }
  \label{fig:pipeline}
\end{figure}

@@

The second step (Fig.~\ref{fig:pipeline}, 3a)
selects one (or more) inference model(s) $I$ from a set of inference models $I_{1},\dots,I_{n}$. 
We define an experiment $X_{i}$ as the combination of 
an inference model $I_{i}$ and the conditions $C_{i}$ 
to actually use it in the inference step.
As a first example, if the generative model is known and standard,
one can specify this as such.
As a second example, if we want to run only the inference
model that fits best to an alignment from a set of candidates,
one can specify this as well (see section 'Candidate models').

@@

Similar to other experiments, \verb;pirouette; allows to do
a control measurement, by use of a process we call twinning. 
In this context, this control results in an error distribution
that is the baseline error of the pipeline. The difference
between the 'true' and 'twin' error distributions is caused only
by the mismatch between the generative tree model and the assumed
tree prior.

The twinning process, $T$, encompasses two steps:
$T_1$, that generates a 'twin tree' (Fig.~\ref{fig:pipeline}, 1b) 
and $T_2$, which generates a 'twin alignment' (Fig.~\ref{fig:pipeline}, 2b).
Both twin tree and alignment will be analyzed in the same way 
as the true tree and alignment.

@@

The user has to specify exactly one standard inference model,
but may be insure which one to pick. To account for this, the user can
specify a set of candidate inference models. After a true alignment
has been simulated, the candidate model with the highest 
evidence (a.k.a. marginal likelihood) will be
used in another inference run, resulting in another error distribution.
The evidence for an inference model is estimated by nested 
sampling [\cite{russel2019model}], using the \verb;NS; BEAST2 package.

If twinning is used, a candidate model that has the highest evidence for
the twin alignment, this model is also used to create another error
distribution. Thanks to the use of candidate models, one can check
if the assumed generative model, has been a good choice.

\subsection{Stochasticity caused by simulating phylogenies}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    The inference error made 
    for an assumed generative tree model and best candidate model,
    compared with the error obtained for the twin tree.
    The assumed generative tree model is the model assumed to be closest to
    the actual generative tree model that generated the true tree.
    The twin distributions show the baseline inference error.
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

Focussing on the upper panel of Figure \ref{fig:example_30},
we can see that the error distributions of the assumed generative model
differ strongly between the true and twin tree. 
This difference shows the extent of the mismatch between
the actual tree model (which is DD) and the (BD) tree prior used.
Because these distributions are distinctively different,
the inference error we make when using an 
incorrect (that is, BD) tree prior on a DD tree
is profound.

@@

The candidate model that had highest evidence given the simulated alignment,
was JC, RLN, BD (see Table \ref{tab:options} for the meaning of these 
abbreviations). JC was indeed the site model used when simulating the
alignments. The RLN clock model is an unexpected choice: the RLN clock
model assumes that mutation rates differ between species, where the
alignment is simulated with equal mutation rates for all species.
The BD model is indeed closer to the DD model than Yule, as both BD and DD
model allow for extinction, where Yule does not.

@@

We showed how to use \verb;pirouette; to quantify the importance of a 
tree prior in Bayesian phylogenetics, assuming the simplest standard 
tree model possible.
In principle any other standard tree model can be assume, 
but we chose to provide the simplest example.

Figure~\ref{fig:example_30} illustrates the primary result of our pipeline: 
it shows the error distributions for the true tree and the twin tree 
when either the generating model or the best candidate model is used in inference. 
The clear difference between the error distributions 
for the true tree and the twin tree suggests 
that the choice of tree prior does matter.
We note, however, that only one tree from a novel tree model
is not enough to determine the impact of using an incorrect
tree prior. Instead, a distribution 
of multiple trees, generated by the novel tree model, should be used.
Also, we think that judging a new tree model by its recovery when using
a standard tree prior is an oversimplification: a new tree model may
still tell us something about an evolutionary aspect such as 
a trait or geography. \verb;pirouette;'s results encourage
to convert this novel tree model into a standard tree prior, 
so that the inference is (as predicted to be) improved strongly.

Interpreting the results of \verb;pirouette; remains a subject 
of study. \verb;pirouette; can quantify these, which is a good
first step, but does not give a unequivocal answer to the question 
if the inference error is profound. Using the nLTT statistic is
a promising starting, as it can compare any two trees and 
results in an error distribution of known range. If a researcher
would be more interested in other aspects such as tree balance,
\verb;pirouette; allows for this.

In conclusion, \verb;pirouette; can show the errors to be expected
when the tree model assumed in inference is different from the 
actual generative tree model.
The user can then judge whether or not a new tree prior, 
tailored to the novel tree model, is needed. 
If this is indeed the case, one has a reason
to implement the novel tree prior as an addition to 
his/her favorite Bayesian inference tool.
